---
title: "Trial"
author: "EunJu Lee"
date: "2021-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
xy = rnorm(100)
```

```{r echo=FALSE}
hist(xy)
```

## R Markdown
<!-- 이부분은 표시되지 않는다(shift+ctrl+c) -->
한글로 보고서=> html형식은 가능하나 pdf형식은 불가능(오류)
또는 html-> open in browser-> pdf로 인쇄

This is an **R Markdown** document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
